Sale difference between Loblaws and Voila

### 2024-11-15 paper/paper.qmd
update paper.qmd

data <- read_csv("../data/clean_data.csv")

```

@@

This research explores the question: **When something's on "sale," was the price artificially increased just before the sale, only to be lowered back to its regular level?** To investigate this, we will analyze historical price data from various grocery vendors to examine patterns preceding and following sales events. By comparing regular and sale prices over time, this study aims to identify any indications of pre-sale price increases, offering insight into whether certain sales are truly beneficial for consumers or merely marketing tactics designed to create a perception of value.

@@

# Appendix {-}

>>>>

data <- read_csv("../data/clean_data.csv")
```

@@

This research explores the question: When something's on "sale," was the price artificially increased just before the sale, only to be lowered back to its regular level?** To investigate this, we will analyze historical price data from various grocery vendors to examine patterns preceding and following sales events. By comparing regular and sale prices over time, this study aims to identify any indications of pre-sale price increases, offering insight into whether certain sales are truly beneficial for consumers or merely marketing tactics designed to create a perception of value.

@@
